Arrows for Parallel Computations

### 2017-07-08 paper/content/benchmarks.tex
removed unnecessary benchmarks

\newcommand{\performancediffplot}[7]{
\begin{tikzpicture}
\begin{axis}[title={#1},
title style={align=center},
xlabel=threads,
xtick={#4},
ytick distance=#6,
minor tick num=9,
ylabel=time (seconds),
grid=both,
legend entries={#2},
legend style={at={(0.5,0.01)},anchor=south},
max space between ticks=50pt,
grid style={line width=.1pt, draw=gray!10},
major grid style={line width=.2pt,draw=gray!50},
xmin=-1,
xmax=#7]
#5
\end{axis}
\end{tikzpicture}
}

@@

\performanceSkelRMSM{4423}{32}

\speedupSkelRMSM{4423}{32}

\performanceSkelRMSM{4423}{64}

\speedupSkelRMSM{4423}{64}

\performanceSkelRMSM{9941}{32}

\speedupSkelRMSM{9941}{32}{32}

\performanceSkelRMSM{9941}{64}

\speedupSkelRMSM{9941}{64}

@@

\performanceSkelRMDist{9941}{256}{16,32,64,128,256,512}{528}

\performanceSkelRMDistDiff{9941}{256}{16,32,64,128,256,512}{0.11}{528}

\speedupSkelRMDist{9941}{256}{16,32,64,128,256,512}{528}

\speedupSkelRMDistDiff{9941}{256}{16,32,64,128,256,512}{528}

\performanceSkelRMDist{11213}{256}{16,32,64,128,256,512}{528}

\performanceSkelRMDistDiff{11213}{256}{16,32,64,128,256,512}{0.1}{528}

\speedupSkelRMDist{11213}{256}{16,32,64,128,256,512}{528}

\speedupSkelRMDistDiff{11213}{256}{16,32,64,128,256,512}{528}

>>>>

\newcommand{\performancediffplot}[7]{
\begin{tikzpicture}
\begin{axis}[title={#1},
title style={align=center},
xlabel=threads,
xtick={#4},
ytick distance=#6,
minor tick num=9,
ylabel=time (seconds),
grid=both,
legend entries={#2},
legend style={at={(0.99,0.99)},anchor=north east},
max space between ticks=50pt,
grid style={line width=.1pt, draw=gray!10},
major grid style={line width=.2pt,draw=gray!50},
xmin=-1,
xmax=#7]
#5
\end{axis}
\end{tikzpicture}
}

@@

%\performanceSkelRMSM{4423}{32}

%\speedupSkelRMSM{4423}{32}

%\performanceSkelRMSM{4423}{64}

%\speedupSkelRMSM{4423}{64}

%\performanceSkelRMSM{9941}{32}

%\speedupSkelRMSM{9941}{32}{32}

%\performanceSkelRMSM{9941}{64}

%\speedupSkelRMSM{9941}{64}

@@

%\performanceSkelRMDist{9941}{256}{16,32,64,128,256,512}{528}

%\performanceSkelRMDistDiff{9941}{256}{16,32,64,128,256,512}{0.11}{528}

%\speedupSkelRMDist{9941}{256}{16,32,64,128,256,512}{528}

%\speedupSkelRMDistDiff{9941}{256}{16,32,64,128,256,512}{528}

%\performanceSkelRMDist{11213}{256}{16,32,64,128,256,512}{528}

%\performanceSkelRMDistDiff{11213}{256}{16,32,64,128,256,512}{0.1}{528}

%\speedupSkelRMDist{11213}{256}{16,32,64,128,256,512}{528}

%\speedupSkelRMDistDiff{11213}{256}{16,32,64,128,256,512}{528}
